Parameterization of the responses of subarctic European vegetation to key environmental variables for ozone risk assessment

### 2022-04-28 VegOzone.tex
REphrase Intro

In Section~\ref{sec:dam}, we give a brief summary of the key components and  drivers of the $\mathrm{DO_3SE}$ model that is used to assess the ozone risk. To study the influence of selected parameters on ozone risk in the subarctic, we propose a method to localize temperature response functions based on climate data and start and end of the growing season from satellite observed gross primary productivity (GPP). For the later discussion of results, we summarize climate and weather conditions of the 2018/19 growing season at our research site in Section~\ref{sec:stats}. Results of the localization, the ozone risk modelling, and the climate perspective are presented in Section~\ref{sec:results}. In Section~\ref{sec:conc}, we discuss these results concerning prevailing conditions and give an outlook on how future assessments of pollution risk in the subarctic could be improved.

>>>>

In Section~\ref{sec:dam}, we give a brief summary of the key components and  drivers of the $\mathrm{DO_3SE}$ model that is used to assess the ozone risk. To study the influence of selected parameters on ozone risk in the subarctic, we propose a method to localize temperature response functions based on climate data and to infer start and end of the growing season from satellite observed gross primary productivity (GPP). Results of the ozone risk modelling are presented in Section~\ref{sec:results}. For evaluating these results, we assess the climate anomaly of weather conditions in the 2018/19 GS at our research site in Section~\ref{sec:stats}. In Section~\ref{sec:conc}, we discuss these results concerning prevailing conditions and give an outlook on how future assessments of pollution risk in the subarctic could be improved.
